% based on the template from Sourabh Bajaj

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{times}
\input{glyphtounicode}

\hypersetup{
    colorlinks=true,
    linkcolor=cyan,
    filecolor=magenta,      
    urlcolor=blue
    }

% \colorlinks=true

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-1pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

 % Variables
 \def \ASP{https://blog.twitter.com/engineering/en_us/topics/infrastructure/2020/building-twitters-ad-platform-architecture-for-the-future}
 \def \ShardLib{https://blog.twitter.com/engineering/en_us/topics/infrastructure/2021/sharding-simplification-and-twitters-ads-serving-platform}
 \def \NextNet{https://avionica.com/wp-content/uploads/2021/03/NEXTNet-avSYNC-product-brochure.pdf}
 \def \OFD{https://www.geaviation.com/systems/avionics/open-flight-deck}
 \def \Patent{https://drive.google.com/file/d/1DsnaAByaBixFv9GfyCH6JUAA95fj8aTY/view}
%-------------------------------------------
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Jesus Sanchez} & \faEnvelope \, \href{mailto:jesus.sanchez@outlook.com}{jesus.sanchez@outlook.com}\\
 \href{https://www.linkedin.com/in/jesus-sanchez-sevilla}{\faLinkedin \, /jesus-sanchez-sevilla}  & \faPhone \, +1-857-320-5056 \\
\end{tabular*}



%-----------EXPERIENCE-----------------
\section{Experience}

  \resumeSubHeadingListStart

    \resumeSubheading
      {Brown Brothers Harriman}{Boston, MA}
      {Senior Software Engineer}{Apr 2023 - Present}
      \resumeItemListStart
        \resumeItem{Data Platform}
          {As part of the \textbf{InfoDataFabric} team, I'm the technical lead for the 3 main services powering client facing applications, driving
          new features, documentation, code quality, testing, automation.
          Designed and implemented team wide error handling strategy, from format definition to }
        \resumeSubHeadingListStart
          \resumeSubItem{Tech stack} {Java, Spring, SQL, Angular, Python}
        \resumeSubHeadingListEnd
      \resumeItemListEnd

    \resumeSubheading
      {Twitter}{Boston, MA}
      {Senior Software Engineer}{Sept 2022 - Jan 2023}
    \resumeSubSubheading
      {Software Engineer}{Dec 2019 - Aug 2022}
      \resumeItemListStart
        \resumeItem{Ads Serving Platform}
          {As part of the \href{\ASP}{Ads Serving Platform} team, I've worked in the re-architecture of the AdServer platform,
          completing the transition to a microservices based architecture and continue its improvement
          in areas like configuration, experimentation and scalability.}
        \resumeSubHeadingListStart
          \resumeSubItem{AdServer}{Led the design and implementation of a rule-based configuration
          system to enable a dynamic ad search and selection pipeline.}
          \resumeSubItem{ShardLib}{Contributed to the implementation of a \href{\ShardLib}{Sharding Library},
          used to simplify the management of sharded microservices in the serving pipeline.}
          \resumeSubItem{Other}{Regular oncall support for some of the main services used in the ad 
          serving pipeline. Collaboration with partner teams in the introduction of new ad products.}
          \resumeSubItem{Tech stack} {Java, Scala, Python, Finatra/Finagle, Thrift}
        \resumeSubHeadingListEnd
      \resumeItemListEnd
      
    \resumeSubheading
      {GE Aviation}{Queretaro, Mexico}
      {Senior Software Engineer}{Apr 2019 - Nov 2019}
      \resumeItemListStart
        \resumeItem{Digital Cloud Solutions}
          {Software Engineer part of a group working in the connected aircraft, leveraging Azure cloud
          and web technologies to process flight data.}
        \resumeSubHeadingListStart
          \resumeSubItem{Connected Aircraft / NEXTNet-avSync}
          {Developed microservices to extract flight data, process it and send it to the cloud 
          (part Avionica's \href{\NextNet}{NEXTNet-avSync}).}
          \resumeSubItem{Other}
          {Collaboration with hardware team to develop APIs to communicate with the backend system.
          Documentation maintenance. Mentor to junior engineers.}
          \resumeSubItem{Tech stack} {Java, Python, Spring, Azure}
        \resumeSubHeadingListEnd
      \resumeItemListEnd
   \resumeSubSubheading
    {Embedded Software Engineer}{May 2014 - Apr 2019}
    \resumeItemListStart
       \resumeItem{Avionics \& Digital Systems}
         {Technical leader for Mexico's team of an IR\&D project that focuses on next-generation 
         flight decks, improving the graphical capabilities of display apps and exploring new ways of human-machine interaction.}
        \resumeSubHeadingListStart
          \resumeSubItem{Virtual OpenGL}
          {Contributed to the design and implementation of a custom graphics API based on OpenGL ES.
          Developed tools to integrate high-level design software with our graphics stack as well as the cross-platform build system for the graphics API}
          \resumeSubItem{Digital Moving Map}
          {Led the development of a digital moving map, designed and build an API for remote drawing, 
          interaction and control, part of the \href{\OFD}{Open Flight Deck} project.}
          \resumeSubItem{RPC System}
          {Designed and implemented a simple RPC system for sending avionics information on top of
          \href{https://zeromq.org/}{ZMQ}, written in C and with client and server APIs for C, Python, C\#, 
          as well as a code generator for transforming JSON formatted data model definition files to 
          ZMQ C API.}
          %\resumeSubItem{Landing Gear System Monitor}
         %{Led the design and development of a landing gear system monitor application, test methodology
         %and integration support at the client's facilities.}
          \resumeSubItem{Other}
          {Conducted global training sessions for users of our Avionics stack, participated in the 
          organization of two successful hackathons directed towards both students 
          and professionals wanting to experience GE's engineering challenges.}
          \resumeSubItem{Tech stack} {C, Python, OpenGL, Yocto}
        \resumeSubHeadingListEnd
    \resumeItemListEnd
   \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Benemerita Universidad Autonoma de Puebla}{Puebla, Mexico}
      {Master of Science in Electronics}{Aug. 2011 -- Jun. 2013}
   \resumeSubSubheading
      {Bacherol of Engineering in Mechatronics}{Aug. 2005 -- May. 2010}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Other Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Autonomous Mobile Robot}
      {\href{https://github.com/datgeezus/mobile_robot}{\faGithub \, mobile\_robot}
      | \, Mobile robot platform for academic research (Patent \textbf{\href{\Patent}{MX/I/2018/100659}}). }
    \resumeSubItem{dsPIC Peripheral Libraries}
      {\href{https://github.com/datgeezus/dspic33f_pic24h_corelibs}{\faGithub \, dspic33f\_pic24h\_corelibs} 
      | \,  Peripheral libraries with support for UART, SPI, I2C, I/O, QEI, Timers, ADC for the PIC24/dsPIC33F 
      family of microcontrollers.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
% \section{Programing skills}
%  \resumeSubHeadingListStart
%    \resumeSubItem{Languages}{Java, Python, Scala, C, C++, Typescript}
%    \resumeSubItem{Technologies/Frameworks}{Finagle, OpenGL, Azure, Git, Yocto, Spring}
%  \resumeSubHeadingListEnd
 
\end{document}